Visualization and analysis of probability distributions of large temporal data

### 2022-02-27 report/response.Rmd

Done.

> Q21. Are parts a and b in Figure 3.8 correctly labeled and also matching with the figure caption? The caption reads For id 1, patterns look similar within weekdays and weekends. Visually, this seems to be the case for id 7 (in part b). This also visually matches Figure 3.7b.

Caption rephrased to make it more clear.

<!-- For id: 7, there is more distributional difference between consecutive hours of the day compared to id:1. Also all the days of the week are different from each other in id:7. id:1 has similar behavior across all days within both weekdays and weekends. For this reason, the wpd for id:7 has a higher value than id:1 as the similar behavior within weekdays and weekends balances out the difference between weekdays and weekends. The display with hod vs wdwnd would have shown higher values of wpd for id:1 (as can be verified from Table 3). -->

@@

> Q22. I didn't ask earlier, but how were the eight households for Section 3.4 being selected? Was this based on a random sample, or manually do obtain rather different energy usage patterns? This should be answered earlier on, but this also should be addressed in the Discussion: What can be expected when working with the full data set of Chapter 2, i.e., about 13,000. You indicate:
A future direction of work is to be able to explore and compare many individuals/subjects together for similar patterns across significant granularities. What would be computationally (and visually) feasible as 13,000 is a few orders of magnitude
higher than the number of eight households used in this example? Clearly, no full answer is expected here, but rather some speculation of what could possibly be done in the future (or what is done in the next chapter).

- To reflect various energy behavior, data for eight homes for Section 3.4 is acquired from friends and colleagues with different professions, lifestyles, and household sizes. This level of data is private, and we thank our friends and colleagues for agreeing to have their data used for this analysis. This is added in the first paragraph of Application.

- A paragraph is added to the Discussion section to incorporate comments on the computational time.

@@

> Q12. It would help the reader to also mention in the caption of Table 4.3 that P-1 & Q-1 and P-2 & Q-2 are identical. I first looked at Figure 4.9 and then at Table 4.3, but if read in the other order, I likely would have been surprised, to see identical values in some of the table rows (without any further explanation).

Done.

> Q13. For the thesis, the work is adequate and meaningful. For a journal paper, I would like to see some of the points outlined in the Discussion being addressed. What happens if this method is applied to the data from the 13,000 customers that were introduced earlier on? As a reader of a journal paper, I would rather like to see limitations of the method proposed here, e.g., if it does not scale up then why it most likely does not scale up. Otherwise, it is hard to assess whether it is worthwhile to try this method for one's own data.

The Discussion section is split into (1) conclusions, and (2) limitations and future research (including a discussion on computational complexity) to address this comment.

<!-- Split into a "Limitation" and "Discussion" section separately detailing the drawbacks. -->

### 2022-02-27 Rmd/03-hakear.Rmd
Q22 Ch3 Juergen

<!-- patterns are interesting and others are not. The subjects for which behaviors across a group of cyclic granularities are similar, could be grouped together as their periodic behavior is similar. to group subjects -->

>>>>

_Computational time _

<!-- A rough estimate of working with $\wpd$ working with two granularities with $(l,m)$ levels: ~(30s - 300s for 6<=l,m<=50) Computing $\wpd$ is computationally more expensive for cyclic granularities with lower levels $\nx,\nf<=5$. -->
<!-- patterns are interesting and others are not. The subjects for which behaviors across a group of cyclic granularities are similar, could be grouped together as their periodic behavior is similar. to group subjects -->
The computation time of $\wpd$ for a cyclic granularity or harmony is determined by its levels. For example, in a harmony with $6 \leq\nx,\nf \leq 50$, the computation time grows with the number of levels and ranges from $30-300$s. $\wpd$ becomes computationally more expensive for cyclic granularities with lower levels $\nx,\nf \leq 5$. It is around $40-50$ minutes for $\nx,\nf = \{2,3\}$. Even with parallel computation, computing $\wpd$ for many individuals and cyclic granularity/harmonies takes a long time. One solution could be to obtain the significant granularities for a smaller number of individuals in order to get a sense of the significant granularities for the context and then computing $\wpd$ only for those granularities for other individuals. <!--For example, in the case of electricity data, the important granularities for most people were *wnwd*, *hod*, *dow*, and *dom*. After this fact has been established for a few people, $\wpd$ can be computed exclusively for these granularities to save time for others.--> However, information may be lost for individuals with different sets of significant granularities. In any case, additional studies may be conducted to speed up the processing of cyclic granularities with low levels.
